Different rules for binocular combination of luminance flicker in cortical and subcortical pathways

### 2023-06-30 manuscript.Rmd
Fixed a typo in the Fig 4 caption

```{r BSratios, fig.cap="Ratio of binocular to monocular response for three data types. These were calculated by dividing the binocular response by the monocular response at each contrast level, using the data underlying Figures 2c, 3c and 3f. Each value is the average of ratio across N=30 participants, and error bars indicate bootstrapped standard errors.", fig.align="center", out.width = '50%', echo=FALSE}

>>>>

```{r BSratios, fig.cap="Ratio of binocular to monocular response for three data types. These were calculated by dividing the binocular response by the monocular response at each contrast level, using the data underlying Figures 2c, 3c and 3f. Each value is the average ratio across N=30 participants, and error bars indicate bootstrapped standard errors.", fig.align="center", out.width = '50%', echo=FALSE}
